Calculate FD

### 2020-09-04 analysis/calc_fd.Rmd
Modify for new biotime format

  species_mat <- data %>%
    group_by(year, id) %>%
    summarise(abun = sum(sum_abundance)) %>%
    ungroup() %>%
    arrange(year) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = abun, values_fill = 0) %>%
    select(-year)

@@

  trait_mat <- data %>%
    select(-c(taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, traitName, 
              biotimeName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(na.omit(.))) > 1) #remove columns that have the same value for all columns

  #get binary variables so they can be excluded from rescaling 
  bin_vars <- map(trait_mat, ~ all(na.omit(.) %in% 0:1))

  trait_mat <- trait_mat %>%
    mutate_at(vars(-c(id, names(bin_vars[bin_vars == TRUE])), -ends_with("5cat")), 
              list(~as.numeric(scale(.)))) %>% #rescale variables, not binary or categorical
    arrange(id) %>%
    column_to_rownames("id")

@@

system.time(fd <- map(plots, get_fd_safe, obs_data = data))
```

>>>>

  species_mat <- data %>%
    select(year, id, year_abun) %>%
    arrange(year) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = year_abun, values_fill = 0) %>%
    select(-year)

@@

  trait_mat <- data %>%
    select(-c(biotimeName, taxa, id_species, plot, year, year_abun, 
              year_biomass, traitName, scientificName, plot_id, study_id)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(na.omit(.))) > 1)  #remove columns that have the same value for all columns

  #get binary variables so they can be excluded from rescaling 
  bin_vars <- map(trait_mat, ~ all(na.omit(.) %in% 0:1))
  bin_vars <- names(bin_vars[bin_vars == TRUE])

  trait_mat <- trait_mat %>%
    mutate_at(vars(-c(id, bin_vars), -ends_with("5cat")), 
              list(~as.numeric(scale(.)))) %>% #rescale variables, not binary or categorical
    mutate_at(vars(bin_vars), as.character(.)) %>%
    arrange(id) %>%
    column_to_rownames("id")

@@

system.time(fd <- map(plots, get_fd_safe, obs_data = data, m = "min", corr = "cailliez"))
```
